\documentclass[10pt]{article}
\usepackage{calc}
\reversemarginpar

\usepackage[paper=letterpaper,
            marginparwidth=1.2in,     % Length of section titles
            marginparsep=.05in,       % Space between titles and text
            margin=1in,               % 1 inch margins
            includemp]{geometry}

\setlength{\parindent}{0in}

\usepackage{paralist}

\usepackage{fancyhdr,lastpage}

\pagestyle{empty}      % Uncomment this to get rid of page numbers
\fancyhf{}\renewcommand{\headrulewidth}{0pt}
\fancyfootoffset{\marginparsep+\marginparwidth}
\newlength{\footpageshift}
\setlength{\footpageshift}
          {0.5\textwidth+0.5\marginparsep+0.5\marginparwidth-2in}
\lfoot{\hspace{\footpageshift}%
       \parbox{4in}{\, \hfill %
                    \arabic{page} of \protect\pageref*{LastPage} % +LP
%                    \arabic{page}                               % -LP
                    \hfill \,}}

% Finally, give us PDF bookmarks
\usepackage{color,hyperref}
\definecolor{darkblue}{rgb}{0.0,0.0,0.3}
\hypersetup{colorlinks,breaklinks,
            linkcolor=darkblue,urlcolor=darkblue,
            anchorcolor=darkblue,citecolor=darkblue}

\newcommand{\makeheading}[1]%
        {\hspace*{-\marginparsep minus \marginparwidth}%
         \begin{minipage}[t]{\textwidth+\marginparwidth+\marginparsep}%
                {\large \bfseries #1}\\[-0.15\baselineskip]%
                 \rule{\columnwidth}{1pt}%
         \end{minipage}}

% Otherwise the top of the section header will not line up with the top
% of the section. Of course, using a single comment character (%) on
% empty lines allows for the function of the first example with the
% readability of the second example.
\renewcommand{\section}[2]%
        {\pagebreak[2]\vspace{1.3\baselineskip}%
         \phantomsection\addcontentsline{toc}{section}{#1}%
         \hspace{0in}%
         \marginpar{
         \raggedright \scshape #1}#2}

% An itemize-style list with lots of space between items
\newenvironment{outerlist}[1][\enskip\textbullet]%
        {\begin{enumerate}[#1]}{\end{enumerate}%
         \vspace{-.6\baselineskip}}

% An itemize-style list with little space between items
\newenvironment{innerlist}[1][\enskip\textbullet]%
        {\begin{compactenum}[#1]}{\end{compactenum}}

% To add some paragraph space between lines.
% This also tells LaTeX to preferably break a page on one of these gaps
% if there is a needed pagebreak nearby.
\newcommand{\blankline}{\quad\pagebreak[2]}

% --- BEGIN CV CONTENT 

\begin{document}
\makeheading{Matti Dahlbom's Curriculum Vitae}

\section{Contact Information}

\begin{tabular}{p{0.4\textwidth}p{0.4\textwidth}}
Armas Launiksen Katu 11 F 81 & 
\textit{GSM:} +358 40 521 6859 \\
02650 ESPOO & 
\textit{e-mail:} \href{mailto:matti@777-team.org}{matti@777-team.org} \\
FINLAND  & 
\textit{WWW:} \href{http://777-team.org/~matti/}{777-team.org/~matti/} \\
\end{tabular}

\section{Date of Birth} 
%
February 8th, 1977

\section{Nationality}
%
Finnish

\section{Military Service}
%
1996-1997, Finnish Navy

\section{Education}

\href{http://www.tkk.fi/}{\textbf{Helsinki University of Technology}} 
\begin{innerlist}
\item[] Master of Science in Computer Science, graduated in 2003
\item[] Major: Interactive Digital Media
\item[] Minor: Telecommunications Software
\item[] Master's Thesis: ``Efficient Molecular Visualization in Large 
Scale Systems''
\end{innerlist}

\section{Languages} 
%
\begin{tabular}[t]{@{}p{2cm}p{2cm}}

Finnish & Native\\
English & Fluent\\
German  & Basics\\
Swedish & Basics
\end{tabular}

\section{Programming languages}
\begin{tabular}[t]{@{}p{5cm}p{6cm}}
C/C++ & Very good (since 1992 ish) \\
Assembler (MIPS, ARM, x86) & Very good (since 1994 ish) \\
Java & Very good (since 1998) \\
Python & Very good (5+ yrs) \\
Objective-C & Good (since 2011) \\
PHP & Very good (10+ yrs) \\
JavaScript + jQuery & Good (5+ yrs) \\
UNIX sh/perl/AWK etc. & Good (10+ yrs) \\
\end{tabular}

\section{Other technical skills}

Operating systems: Linux/Unix, Symbian, Windows, MacOS \\
Markups: (X)HTML, CSS, XML/XSLT, \LaTeX{} \\
Mobile OSs: Maemo/MeeGo, iOS, Android, Tizen, Sailfish, Symbian \\
SQL: Oracle, Solid, MySQL, Postgre, MSSQL, SQLite \\
Editors, Frameworks \& environments: Emacs, all major IDEs, Qt, STL, libusb, SDL, OpenGL (ES), Java frameworks, Django, Google AppEngine etc.

\pagebreak
\section{Work History}

\textbf{Yhteysmedia Oy 1997-1998}
\begin{outerlist}
\item[] \textit{Software designer} \\  \\
C/Visual Basic development, support framework/toolset creation.
\end{outerlist}

\blankline

\textbf{ICL Data (later: ICL Invia) 1998-2000}
\begin{outerlist}
\item[] \textit{Software designer} \\ \\
C++ development for a large connectivity software suite. Java development for 
Servlet-based web interfaces. 
\end{outerlist}

\blankline

\textbf{Mermit Business Applications 2000-2007}
\begin{outerlist}
\item[] \textit{Senior software designer} \\ \\
Several embedded systems architect/development tasks with Symbian / Linux. 
Design and implementation of various C++/PHP/J2SE/J2EE projects.
Technical lead role in several projects.
\end{outerlist}

\blankline

\textbf{Ixonos Plc 2007-2011}
\begin{outerlist}
\item[] \textit{Senior consultant} \\ \\
Various projects in the embedded / mobile world dealing with Linux / Symbian.
Some Android tasks.
Occasional consultancy visits to backend Java projects.
Technical lead / architect role in several projects.
\end{outerlist}

\blankline

\textbf{Qvik Oy 2011-present}
\begin{outerlist}
\item[] \textit{Software Architect} \\ \\
Software architectural tasks for both mobile and supporting backend systems.
Implementation work in all kinds of project.
\end{outerlist}

\section{Secondment experience abroad}
Worked for 9 months in Berlin, Germany, in various tasks with a mobile navigation
software suite in 2008-2009.

\section{Freetime projects}
I am constantly working on a software project of some sort on my free time.
Some of the projects past and present can be found here:
\href{http://777-team.org/~matti/software/}{http://777-team.org/~matti/software/}

\section{Hobbies}

Other hobbies besides programming 
include freeride skiing, travelling, diving, occasional team sports, 
trekking and 
bowling as well as Nethack, in which I ascended in early 2011.

\section{Updated} 
May 31st, 2012

\end{document}
